Discussion

### 2023-03-08 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
first limitation

Our findings must be considered in light of several limitions.

>>>>

Our findings must be considered in light of several limitations.
First, it must be mentioned that a block design was used.
This is important for two reasons: first, because this allows for habituation effects of EMG activity within the block, and second, because this is how the subjective ratings were made retrospectively.
This may have led to the fact that the correlations we found between SVs and predictors were lower than if we had used an event-related design.
However, block designs are common in ER research [@Barreiros2019] and were used in previous studies [@Scheffel2019].
Furthermore, we were able to confirm our manipulation checks, indicating that implementation of ER strategies was successful, both on subjective and physiological levels.s
